Comparing OTU quality across clustering strategies

### 2021-07-16 exploratory/2021/algorithm_diagram.Rmd
Format seq colors for ggtext

```{r pseudo_optifit}
reticulate::source_python(here('code', 'py', 'algorithm_diagram.py'))
optifit_iters <- run_optifit() %>% 
  sapply(function(x) {
    return(list(nodes = x[['nodes']] %>% py_to_r(),
                edges = x[['edges']] %>% py_to_r()))
    })
```

```{r graph_optifit, fig.dim=c(6,5), dpi=300}
g <- tbl_graph(nodes = optifit_iters[,1]$nodes,
               edges = optifit_iters[,1]$edges %>% 
                 mutate(is_loop = from == to))
plot_graph(g)
```

>>>>

```{r pseudo_optifit}
reticulate::source_python(here('code', 'py', 'algorithm_diagram.py'))
optifit_iters <- run_optifit() %>% 
  lapply(function(x) {
    return(list(nodes = x[['nodes']] %>% py_to_r(),
                edges = x[['edges']] %>% py_to_r() %>% 
                 mutate(is_loop = from == to)))
    })
```

```{r optifit_example, fig.dim=c(6,5), dpi=300}
g <- tbl_graph(nodes = optifit_iters[[1]]$nodes,
               edges = optifit_iters[[1]]$edges)
plot_graph(g)
```

```{r plot_optifit_iters, fig.dim=c(6,5), dpi=300}
lapply(optifit_iters, function(x) {
  tbl_graph(nodes = x$nodes, edges = x$edges) %>% 
    plot_graph()
}) %>% 
  wrap_plots(ncol = 1)
```
